Which spherical CNN should you use?\\ DeepSphere V2

### 2019-07-19 main.tex
general story

\begin{abstract}
No
\end{abstract}

\section{Introduction [2 pages]}
Get inspiration from DeepSphere V1

Why are spherical CNNs important? What are the application?
See DeepSphere workshop paper

Desiderata:
* respect the domain
  * rotational equivariance
  * deformation (e.g., on the icosahedron for gauge)
* powerful / generality => isotropic vs anisotropic
* scale: computational cost \& memory usage (feature maps)
* flexible (samplings, irregular), simplicity (implementation)

@@

Present the different spherical CNNs with pro and cons => mostly scale vs generality
* 2D CNN => doesn't respect geometry and equivariance
* Cohen spherical CNN => most general, but doesn't scale
* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)
* Esteves => ?
* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)

\cite{perraudin2019deepsphere}

\section{Method [2 pages]}

* HEALPix: improvement from DeepSphere v1
* equiangular: Renata \& Pascal

\section{Rotation equivariance [2 pages]}
\subsection{Link with the Laplace-Beltrami Operator}

@@

\section{Experiments [2 pages]}

@@

* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed
* cannot compare with Mudigonda (16 vs 1 input channel)
* full: we scale => lead to better perf?

\section{Conclusion}

* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.
  * Not the most general, but sufficient empirically
  * scales linearly => cannot do better ($n^1.25$ for HEALPix)
  * flexible => independent of the sampsamples can be 
* anisotropy (most general) doesn't help. research question: when can it be useful?

future work:
* when anisotropy needed?
* irregular sampling while respecting the geometry
* beyond the sphere, any manifold

@@

\appendix
\section{Appendix}

\subsection{}

>>>>

\begin{abstract}
story / main point:

* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\

contributions:\\
* theory => convergence (better graph)\\
* experiments on relevant problems (not spherical MNIST) => check the desiderata\\
  * surprising: anisotropy doesn't seem useful\\

\end{abstract}

\section{Introduction [2 pages]}
Get inspiration from DeepSphere V1\\

Why are spherical CNNs important? What are the application?\\
See DeepSphere workshop paper\\

Desiderata:\\
* respect the domain\\
  * rotational equivariance\\
  * deformation (e.g., on the icosahedron for gauge)\\
* powerful / generality => isotropic vs anisotropic\\
* scale: computational cost \& memory usage (feature maps)\\
* flexible (samplings, irregular), simplicity (implementation)\\

@@

On the one side, we have Cohen which is computationally very expensive but perfectly equivariant, on the other we have cube sphere which computationl very good but not equivariant at all. Other methods are tradedoff between these two. What is a good tradeoff? We think that DeepSphere is

Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
* 2D CNN => doesn't respect geometry and equivariance\\
* Cohen spherical CNN => most general, but doesn't scale\\
* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
* Esteves => ?
* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\

\section{Method [1 pages]}

* HEALPix: improvement from DeepSphere v1 \cite{perraudin2019deepsphere}
* equiangular: Renata \& Pascal

\section{Rotation equivariance [2.5 pages]}

\subsection{Link with the Laplace-Beltrami Operator}

@@

\subsection{Equivariance error}

* define a measure of equiv error\\
* show convergence empirically\\
* improved upon V1\\
* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\

\section{Experiments [2 pages]}
Which experience show that DeepSphere V1 and V2 are equivalent in practice.

@@

* small: better perf than gauge and Jiang. due to icosahedron distortion? to be confirmed\\
* cannot compare with Mudigonda (16 vs 1 input channel)\\
* full: we scale (50B pixels, 20TB) => lead to better perf?\\

\subsection{GHCN}

* task is artificial, but it shows DeepSphere's flexibility\\
* structure (looking around) help for prediction\\

\section{Conclusion [0.5 pages]}

* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
  * scales linearly => cannot do better ($n^1.25$ for best HEALPix, linear for not optimal)\\
  * flexible => independent of the sampling\\

future work:\\
* when anisotropy useful? (research question)\\
* irregular sampling while respecting the geometry\\
* beyond the sphere, any manifold\\

@@

{\LARGE \sc {Title of the paper: Supplementary Material}}
\appendix
\section{Proof of theorem}

\section{Experiments details}
